How is experience transformed into memory?

### 2018-08-27 paper/main.tex
updated code and added one more ref

Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}. This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall. Our approach is fundamentally different. We ask: which brain regions during movie viewing match the movie structure and how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)? This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory. In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12}. One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene. MTL activity patterns also matched participant's recall, which is consistent with a large body of literature highlighting the role of the MTL in episodic memory encoding ~\citep{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.

>>>>

Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}. This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall. Our approach is fundamentally different. We ask: which brain regions during movie viewing match the movie structure and how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)? This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory. In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}. One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene. MTL activity patterns also matched participant's recall, which is consistent with a large body of literature highlighting the role of the MTL in episodic memory encoding ~\citep{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
